Preregistration, design, IRB

### 2018-04-20 preregistration.Rmd
Add IRB approval forms

We will preregister this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).

<p><a href="#" class="btn btn-primary btn-md btn-success disabled" target="_blank">
<i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
OSF preregistration protocol &raquo;
</a></p>

We will also participate in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:

@@

This project has received IRB approval from the human subjects research committees at both Duke and Dartmouth. We have included a generic version of our protocol below.

<p><a href="files/duke-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
Duke IRB approval
</a> 
&nbsp;
<a href="#" class="btn btn-primary btn-md btn-success disabled" target="_blank">
<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
Dartmouth IRB approval
</a></p>

>>>>

We preregistered this study with the [Center for Open Science's](https://cos.io/) [Open Science Framework](https://osf.io/).

<p><a href="https://osf.io/dx973/register/565fb3678c5e4a66b5582f67" class="btn btn-primary btn-md btn-success" target="_blank">
<i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
OSF preregistration protocol &raquo;
</a></p>

We are participating in COS's [Preregistration Challenge](https://cos.io/our-services/prereg-more-information/), and will submit our final article to one of the following eligible journals:

@@

This project has received IRB approval from the human subjects research committees at both BYU and Christopher Newport. We have included a generic version of our protocol below.

<p><a href="files/byu-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
BYU IRB approval
</a> 
&nbsp;
<a href="files/cnu-irb-approval.pdf" class="btn btn-primary btn-md btn-success" target="_blank">
<i class="fa fa-check-circle" aria-hidden="true"></i>&nbsp;
Christopher Newport IRB approval
</a></p>

\
